---
title: "Getting started"
author: "Colin Gillespie"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Getting started}
-->
  
## Installing the package

The package lives on [github](https://github.com/csgillespie/voltagefit/) and can be installed using

```{r eval=FALSE}
devtools::install_github("csgillespie/voltagefit")
```
and loaded in the usual way
```{r, message=FALSE}
library("voltagefit")
```

To enable parallelisation, run
```{r eval=FALSE}
library("doParallel")
registerDoParallel()
```

## Example data

The package contains some example data sets that can be accessed via
```{r}
data_dir = system.file("extdata/", package="voltagefit")
list.files(data_dir)
```

ID | Week 
---|------
3737 | 1
3757 | 1
3758 | 1
3759 | 1
4464 | 2
4465 | 2

## A single wafer

We can load a single wafer from the package via

```{r}
## This is just a data frame. 
## I expect the data will come from a database
wafer_3737 = readRDS(file.path(data_dir, "3737.rds"))
```
To fit the model to a single wafer, we use `fit_wafer`
```{r}
fit_3737 = fit_wafer(wafer_3737, verbose=FALSE)
fit_3737
```
The object `fit_3737` is a data frame, with `r ncol(fit_3737)` columns and 
`r nrow(fit_3737)` rows. Each row corresponds to a particular curve on the wafer. The
columns are

  * `id`: a unique idenfier for the wafer;
  * `cost`: the error term from the curve fitting process;
  * `direction`: `Forward` or `Backward`
  * `X1`, ..., `X6`: Parameters relating to the logistic model.

## Multiple wafers

First load in example data. The data corresponds 
```{r}
data_dir = system.file("extdata/", package="voltagefit")
## In real life, pull data from a database
all_wafers = fit_all(data_dir, verbose=FALSE)
```
You can also view the parameters
```{r, fig.keep="none"}
plot(all_wafers, cost=FALSE)
hist(all_wafers)
```

## Design matrix

For each voltage curve, we have fitted a logistic model, obtained parameter estimates
and estimated how well the curve fits. This next stage attempts to estimate
week and treatment effects. Using the data in `all_wafers`, we first create a design
matrix descriping the experimental set-up. The design matrix should have
three columns

```{r}
wafer = unique(all_wafers$id)
week = c(1, 1, 1, 1, 2, 2)
treatment = rep(1, 6)
(design = data.frame(wafer = wafer, week = week, treatment = treatment))
```
We then fit a MANOVA model, using the parameter values as the response
```{r}
fit_man = fit_manova(all_wafers, design)
(params = get_params(fit_man))
```
<!-- MANOVA is just a multivariate version of the ANOVA table. As such, we can  -->
<!-- obtain a $p$-value for week differences using -->
<!-- ```{r, results="hide"} -->
<!-- #fit_man$forward$man_w -->
<!-- #summary(fit_man$backward$man_w) -->
<!-- ``` -->


We can now get the mean parameters
```{r}
means = mean(fit_man)
```
and plot them
```{r,fig.width = 8}
library(ggplot2)
ggplot(means) + geom_line(aes(x, y, colour=type)) + scale_y_log10() + 
  facet_grid(~direction)
```

```{r,fig.width = 8}
## Generate a sample of parameters for the underlying curve
unders = sample(fit_man,  n=20)
#head(unders)

#unders = dd
ggplot(unders$samples) + 
  geom_line(aes(x, y, group=sim_no, colour=type)) + scale_y_log10() + 
  facet_grid(~direction)

```

