---
title: "Getting started"
author: "Colin Gillespie"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Getting started}
-->
  
## Installing the package

The package lives on [github](https://github.com/csgillespie/voltagefit/) and can be installed using

```{r eval=FALSE}
devtools::install_github("csgillespie/voltagefit")
```
and loaded in the usual way
```{r, message=FALSE}
library("voltagefit")
```

To enable parallelisation, run
```{r eval=FALSE}
library("doParallel")
## This sets the number of cores to use.
no_of_cores = max(parallel::detectCores() - 1, 1)
registerDoParallel(no_of_cores)
```

## Example data

The package contains some example data sets that can be accessed via
```{r}
data_dir = system.file("extdata/", package="voltagefit")
list.files(data_dir)
```

ID | Week 
---|------
3737 | 1
3757 | 1
3758 | 1
3759 | 1
4464 | 2
4465 | 2

## A single wafer

The package comes with a large number of example data sets. To avoid polluting the
global name space, we're going to load them into their own environment, `e`

```{r}
e = new.env()
data("voltage", package="voltagefit", envir = e)
ls(envir = e)
```
To fit the model to a single wafer, we use `fit_wafer`
```{r}
wafer_5210 = fit_wafer(get("wafer5210", envir=e))
```
The object `fit_5507` is a data frame, with `r ncol(fit_5507)` columns and 
`r nrow(fit_5507)` rows. Each row corresponds to a particular curve on the wafer. The
columns are

  * `id`: a unique idenfier for the wafer;
  * `cost`: the error term from the curve fitting process;
  * `direction`: `Forward` or `Backward`
  * `X1`, ...: Parameters relating to the model.

## Multiple wafers

First load in example data. The data corresponds 
```{r, message=FALSE}
l = lapply(ls(envir = e), 
           function(i) fit_wafer(get(i, envir=e)))
all_wafers = Reduce(rbind, l)
```
You can also view the parameters
```{r,fig.width = 8}
plot(all_wafers)
hist(all_wafers)
```

## Design matrix

For each voltage curve, we have fitted a logistic model, obtained parameter estimates
and estimated how well the curve fits. This next stage attempts to estimate
week and treatment effects. Using the data in `all_wafers`, we first create a design
matrix descriping the experimental set-up. The design matrix should have
three columns

```{r}
wafer = unique(all_wafers$id)
week = c(rep(1:2, each=8), 1)
treatment = rep(1, 17)
(design = data.frame(wafer = wafer, week = week, treatment = treatment))
```
We then fit a MANOVA model, using the parameter values as the response
```{r}
fit_man = fit_manova(all_wafers, design)
(params = get_params(fit_man))
```
MANOVA is just a multivariate version of the ANOVA table. As such, we can
obtain a $p$-value for week differences using
```{r}
fit_man$forward$man_w
#summary(fit_man$backward$man_w)
```

We can now get the mean parameters
```{r}
means = mean(fit_man)
```
and plot them
```{r,fig.width = 8}
library("ggplot2")
#colnames(means)[1:2] = c("VG", "ID")
ggplot(means) + geom_line(aes(VG, ID, colour=type)) + scale_y_log10() + 
  facet_grid(~direction)
```

```{r,fig.width = 8}
## Generate a sample of parameters for the underlying curve
unders = sample(fit_man,  n=20)
ss = trans_device(unders$samples)
ss = unders$samples
ggplot(ss) + 
  geom_line(aes(VG, ID, group=sim), alpha=0.1) + scale_y_log10() + 
  facet_grid(type~direction) +
  geom_line(data=means, aes(VG, ID), colour="steelblue")
```

