---
title: "Getting started"
author: "Colin Gillespie"
output: rmarkdown::html_vignette
---
<!--
%\VignetteEngine{knitr::rmarkdown}
%\VignetteIndexEntry{Getting started}
-->
  
```{r echo=FALSE}  
suppressPackageStartupMessages(library(ggplot2))
theme_set(theme_bw())
```
## Installing the package

The package lives on [github](https://github.com/csgillespie/voltagefit/) and can be installed using

```{r eval=FALSE}
devtools::install_github("csgillespie/voltagefit", build_vignettes = TRUE)
```
and loaded in the usual way
```{r, message=FALSE}
library("voltagefit")
```

To enable parallelisation, run
```{r eval=FALSE}
library("doParallel")
## This sets the number of cores to use.
no_of_cores = max(parallel::detectCores() - 1, 1)
registerDoParallel(no_of_cores)
```
If this step is ommitted, then the package will only use a single core when fitting.

## A single wafer

The package comes with a large number of example data sets. To avoid polluting the
global name space, we're going to load them into their own environment, `e`

```{r}
e = new.env()
data("voltage", package="voltagefit", envir = e)
ls(envir = e)
```
The wafer object is just a data frame
```{r}
head(get("wafer5210", envir = e), 3)
```
The key columns are `wafer_id`, `id`, `ID` and `VG`. 

To fit the model to a single wafer, use the `fit_wafer()` function
```{r, echo=1, eval=FALSE}
wafer_5210 = fit_wafer(get("wafer5210", envir = e))
saveRDS(wafer_5210, file = "wafer_5210.Rds")
```
```{r echo=FALSE}
wafer_5210 = readRDS(file = "wafer_5210.Rds")
```
The object `wafer_5210` is a data frame, with `r ncol(wafer_5210)` columns and 
`r nrow(wafer_5210)` rows. The columns are:

  * `id`: a unique idenfier for the wafer (the `wafer_id`);
  * `cost`: the error term from the curve fitting process;
  * `direction`: `Forward` or `Backward`
  * `X1`, ...: Parameters relating to the model.

## Multiple wafers

First load in example data. The data corresponds 
```{r, message=FALSE, eval=FALSE, echo=1:2}
l = lapply(ls(envir = e), 
           function(i) fit_wafer(get(i, envir = e)))
all_wafers = Reduce(rbind, l)
saveRDS(all_wafers, file="all_wafers.Rds")
```
```{r echo=FALSE}
all_wafers = readRDS(file="vignettes/all_wafers.Rds")
```
You can also view the parameters
```{r,fig.width = 8}
plot(all_wafers)
hist(all_wafers)
```

## Design matrix

For each voltage curve, we have fitted a logistic model, obtained parameter estimates
and estimated how well the curve fits. This next stage attempts to estimate
week and treatment effects. Using the data in `all_wafers`, we first create a design
matrix descriping the experimental set-up. The design matrix should have
three columns

```{r}
wafer = unique(all_wafers$id)
week = c(rep(1:2, each=8), 1)
treatment = c(rep(1, 9), rep(2,8))
(design = data.frame(wafer = wafer, week = week, treatment = treatment))
```
We then fit a MANOVA model, using the parameter values as the response
```{r}
fit_man = fit_manova(all_wafers, design)
(params = get_params(fit_man))
```
MANOVA is just a multivariate version of the ANOVA table. As such, we can
obtain a $p$-value for week differences using
```{r}
summary(fit_man$forward$man_w)
```
However, your sample size will often be two small to get p-values.

## Mean and plausible curves

We can extract average curves for each treatment/week combination
```{r}
means = mean(fit_man)
```
and plot them
```{r,fig.width = 8}
library("ggplot2")
ggplot(means) + 
  geom_line(aes(VG, ID, colour=type)) + scale_y_log10() + 
  facet_grid(~direction)
```
Similarly, we can simulate plausible values
```{r,fig.width = 8}
## Generate a sample of parameters for the underlying curve
unders = sample(fit_man, n = 20)
ss = unders$samples
ggplot(ss) + 
  geom_line(aes(VG, ID, group=sim), alpha=0.1) + scale_y_log10() + 
  facet_grid(type~direction) +
  geom_line(data=means, aes(VG, ID), colour="steelblue")
```
We can also graphically compare curves
```{r}
#treatment2 - baseline
curve_d = curve_diff_mean(fit_man, type=c("baseline", "treatment2"), direction="Forward")
ggplot(curve_d, aes(VG, diff)) + 
  geom_line()
```
Similarly, with uncertainity
```{r}
#treatment2 - baseline
curve_d = curve_diff_sample(fit_man, type=c("baseline", "treatment2"), n = 40,  
                          direction = "Forward")
ggplot(curve_d, aes(VG, diff)) + 
  geom_line(aes(group = sim), alpha=0.05) + 
  stat_smooth()
```





